\include{header}

\firstname{Marlena} % Your first name
\familyname{Bannick} % Your last name

\mobile{+1-206-498-0046}
\email{mnorwood@uw.edu}
\social[github]{mbannick}
\homepage{www.marlenabannick.com}

\begin{document}

\makecvtitle
\vspace{-0.3 in}
\section{Research Interests}
\begin{multicols}{2}
\begin{itemize}
	\item Clinical trials design and methods
	\item Statistical learning for population health applications
	\item Health metrics
	\item Software engineering and statistical computing
\end{itemize}
\end{multicols}


\section{Education}

\cventry{2020--present}{Doctor of Philosophy in Biostatistics}{University of Washington}{}{}{Advised by Dr. Noah Simon and Dr. Ting Ye}

\cventry{2016--2019}{Master of Science in Biostatistics}{University of Washington}{}{}{
Committee: Dr. Ruth Etzioni chair; Dr. Megan Othus \\ 
Thesis: Estimating time to intermediate endpoints using population-level survival data and deconvolution methods, with application to cancer progression and recurrence
}

\cventry{2012--2016}{Bachelor of Science in Public Health}{University of Washington}{}{}{
    Minor in Mathematics; College Honors \\
    \textit{magna cum laude}; Phi Beta Kappa
}

\section{Honors and Awards}

\cvitem{2019}{\href{https://www.biostat.washington.edu/news/congratulations-our-2019-biostatistics-graduates}{Senior MS in Biostatistics Award}, Department of Biostatistics, University of Washington}
\cvitem{2019}{Graduate School Conference Travel Award, University of Washington}
\cvitem{2016}{\href{https://www.washington.edu/husky100/year/2016/#name=marlena-norwood}{Husky 100 Award}, University of Washington}
\cvitem{2016}{\href{https://sph.washington.edu/about/sph-awards-archive}{Outstanding Student Award}, School of Public Health, University of Washington}

\section{Experience}

\cventry{10/2020--present}{Research Assistant}{Fred Hutchinson Cancer Research Center}{}{}{
Supervisor: Dr. Fei Gao
\vspace{1mm}
\begin{itemize}
    \item Working on statistical methods for estimating counterfactual incidence for the placebo arm in HIV prevention trials for a variety of trial designs
    \item Deriving theoretical results, running simulation studies, and preparing manuscripts
\end{itemize}
}

\cventry{2020-2021}{Graduate Trainee}{Institute for Health Metrics and Evaluation}{}{}{
Supervisor: Dr. Aleksandr Aravkin
\vspace{1mm}
\begin{itemize}
    \item Consulting on statistical methods for health metrics applications and engineering projects
    \item Preparing technical papers on statistical methods for health metrics applications
\end{itemize}
}

\cventry{2019--2020}{Mathematical Sciences Researcher}{Institute for Health Metrics and Evaluation}{}{}{
Supervisor: Dr. Aleksandr Aravkin
\vspace{1mm}
\begin{itemize}
    \item Develop quantitative methods and modeling strategies that incorporate all possible relevant global health data to achieve credible and policy-relevant results
    \item \href{https://github.com/ihmeuw-msca}{Implement methods into code} that address analytical challenges across teams at IHME
    \item Lead Python software developer for a \href{https://github.com/ihmeuw/cascade-at}{multi-stage hierarchical disease dynamics model}
    \item Translate quantitative methodology to IHME research teams through consultations
    \item Built \href{https://github.com/ihmeuw/covid-model-seiir-pipeline}{COVID-19 modeling software} for the \href{https://covid19.healthdata.org/projections}{IHME COVID-19 projections}
\end{itemize}
}

\cventry{2016--2019}{Post Bachelor Fellow}{Institute for Health Metrics and Evaluation}{}{}{
Supervisors: Dr. Stephen Lim, Dr. Kyle Foreman, Dr. Theo Vos
\vspace{1mm} \\
\textit{Central Computation for the \href{http://www.healthdata.org/gbd}{Global Burden of Disease Study}}
\vspace{1mm}
\begin{itemize}
    \item Backend development for the institutional statistical modeling program to make \href{https://vizhub.healthdata.org/cod/}{ cause of death estimates} for the Global Burden of Disease Study 2017 and 2019
    \item Designed software for a large cluster computing platform used by dozens of disease modelers as a key part of the GBD estimation pipeline
\end{itemize}
\vspace{1mm} \\
\textit{Natural Language Processing Applications}
\vspace{1mm}
\begin{itemize}
    \item Developed a tool to screen the results of PubMed queries for relevance to research teams at IHME using natural language processing and deep learning methods
\end{itemize}
\vspace{1mm} \\
\textit{Disease Estimation for the \href{http://www.healthdata.org/gbd}{Global Burden of Disease Study}}
\vspace{1mm}
\begin{itemize}
    \item Developed estimates of \href{http://ihmeuw.org/56tv}{non-fatal injury burden} for the Global Burden of Disease Study 2016 and \href{http://ihmeuw.org/56tu}{sexual violence indicators} for the Sustainable Development Goals
\end{itemize}
}

\cventry{2015--2016}{Research Assistant}{Fred Hutchinson Cancer Research Center}{}{}{
Supervisor: Dr. Beth Mueller
\vspace{1mm}
\begin{itemize}
    \item Performed statistical analyses for a cohort study of pregnancy outcomes in women with multiple sclerosis, and a \href{https://doi.org/10.1371/journal.pone.0179006}{case-control study of congenital malformations and childhood cancer}
    \item Researched the capacity of each state in the U.S. to link birth certificates to state cancer registries for a National Cancer Institute-funded study
\end{itemize}
}

\cventry{06--09/2015}{Research Assistant}{Department of Biostatistics, University of Washington}{}{}{
Supervisor: Dr. James Hughes
\vspace{1mm}
\begin{itemize}
    \item Developed a statistical method to estimate under-reporting of sensitive, self-reported behaviors in a study population with biomarkers
    \item \href{https://doi.org/10.1016/j.annepidem.2016.07.011}{Authored a publication on the novel method} that was ultimately presented by Dr. Hughes at the CDC Expert Consultation on Advancing Methods for Biobehavioral Surveys in 2018
\end{itemize}
}

\cventry{06--08/2014}{Research Assistant}{Fred Hutchinson Cancer Research Center}{}{}{
Supervisor: Dr. Deborah Donnell, HIV Prevention Trials Network
\vspace{1mm}
\begin{itemize}
    \item Developed an R program for an HIV Prevention Trials Network study to inform the categorization of biological specimens in a way that optimized sensitivity and specificity
\end{itemize}
}

\cventry{04--08/2014}{Undergraduate Research Assistant}{University of Washington}{}{}{
Center for Clinical and Epidemiological Research
\vspace{1mm}
\begin{itemize}
    \item Supported the maintenance of a large health research registry
    \item Performed targeted literature reviews to inform grants for new epidemiological twin studies
\end{itemize}
}

\cventry{2013--2014}{Undergraduate Research Assistant}{University of Washington}{}{}{
Supervisor: Dr. Suzanne Kerns, Division of Public Behavioral Health and Justice Policy
\vspace{1mm}
\begin{itemize}
    \item Analyzed qualitative survey data using ATLAS.ti to determine barriers to implementing evidence-based parenting interventions in Washington State
    \item Designed online data collection platforms for intervention monitoring and evaluation
    \item Assisted in writing monitoring and evaluation progress reports for the Washington State Division of Behavioral Health and Recovery
\end{itemize}
}

\section{Teaching}

\subsection{Teaching Assistant}

\cvitem{Winter 2021}{BIOST/EPI 537: Survival Data Analysis in Epidemiology, for Prof Jon Wakefield, University of Washington, Seattle. \href{https://github.com/mbannick/survival-discussion-section}{https://github.com/mbannick/survival-discussion-section}}

\cvitem{Spring 2021}{BIOST/STAT 524: Design of Medical Studies, for Prof Tom Fleming, University of Washington, Seattle.}

\cvitem{07/2021}{Supervised Methods for Statistical Machine Learning, for Profs Ali Shojaie and Noah Simon, Summer Institute in Statistics for Big Data, University of Washington.}

\cvitem{05/2022}{Workshop on Statistical Machine Learning, for Prof Noah Simon, ICES Ontario (remote).}

\cvitem{07/2022}{Causal Inference with Observational Data: Common Designs and Statistical Methods, for Profs Ting Ye and Qingyuan Zhao, Summer Institute in Statistics for Clinical \& Epidemiological Research, University of Washington.}

\subsection{Guest Lectures}

\cvitem{07/2020}{"Introduction to Epidemiological and Biostatistical Thinking", Neurology Clinical Fellowship Didactics \textit{Instructor: Dr. Andrea Cheng-Hakimian}, University of Washington, Seattle. \href{https://github.com/mbannick/uw-neurology-fellows}{https://github.com/mbannick/uw-neurology-fellows}}

\cvitem{08/2018 \& 2019}{"Cause of Death Ensemble Model (CODEm)", Global Burden of Disease (GH 590) \textit{Instructor: Dr. Jeffrey Stanaway}, Department of Global Health, University of Washington, Seattle}.

\subsection{Workshops}

\cvitem{09/2020}{"Introduction to Research at the Institute for Health Metrics and Evaluation: Training Bootcamp for First-Year Post-Bachelor Fellows". Designed curriculum and facilitated a week-long crash course on intro epidemiology, biostatistics, R, Git and high performance computing. Institute for Health Metrics and Evaluation, University of Washington, Seattle.}

\cvitem{05/2019}{"Data to DALYs: Case Study on Diabetes", with Dr. Theo Vos and Dr. Liane Ong. 2-day short course. Global Burden of Disease Workshop, Eretria, Greece.}

\subsection{Tutoring}
\cvitem{Fall 2020}{Medical Biometry I (BIOST 511), University of Washington, Seattle}

\section{Publications}

% \subsection{In Preparation}
% \vspace{0.10cm}
% \nocite{*}
% \printbibliography[type=article, heading=none, keyword={prep}]
% \vspace{0.25cm}

% \subsection{Preprints}
% \vspace{0.10cm}
% \nocite{*}
% \printbibliography[type=article, heading=none, keyword={preprint}]
% \vspace{0.25cm}

% \subsection{Submitted}
% \vspace{0.10cm}
% \nocite{*}
% \printbibliography[type=article, heading=none, keyword={submitted}]
% \vspace{0.25cm}

\subsection{Methodological}
\vspace{0.10cm}

\printbibliography[type=article, heading=none, keyword={methods}]
\vspace{0.25cm}

\subsection{Collaborative}
\vspace{0.10cm}
\printbibliography[type=article, heading=none, keyword={collab}]
\vspace{0.25cm}

\subsection{Global Burden of Disease Collaboration}
\cvitem{}{Included as an author on the following publications as part of the \href{https://www.thelancet.com/gbd}{Global Burden of Disease Study}. Developed statistical and computational machinery and performed analyses.}
\vspace{0.10cm}
\printbibliography[type=article, heading=none, keyword={GBD}]

\section{Presentations}

\nocite{*}
\printbibliography[type=misc,heading=none]

\section{Service and Affiliations}

\subsection{Affiliations}
\cvitem{2019--present}{American Statistical Association}

\subsection{Peer Review}
\cvitem{2021}{International Journal of Epidemiology}
\cvitem{2020, 2021}{Machine Learning in Public Health Workshop, NeurIPS}
\cvitem{2020}{Journal of Medical Internet Research}

\subsection{Committees}
\cvitem{2022}{Graduate Program Admissions, UW Biostatistics}
\cvitem{2021}{Open-rank Faculty Search Committee, UW Biostatistics}
\cvitem{2020, 2021}{Equity, Diversity, and Inclusion Committee, UW Biostatistics}
\cvitem{2020}{Educational Policy and Teaching Evaluation Committee, UW Biostatistics}

\section{Additional Training}
{\small
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvitem{2015}{Summer Institute in Statistics and Modeling in Infectious Diseases, University of Washington}

\cvitem{2015}{Writing in the Sciences, \textit{with distinction}, via Stanford Online, Lagunita}

\par}

\end{document}



